\documentclass{article} 
\usepackage[utf8]{inputenc} 
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{framed}
\definecolor{shadecolor}{rgb}{1,0,0}
\newcommand{\figautorefname}{figure}
\newcommand{\secautorefname}{section}
\newcommand{\subsecautorefname}{subsection}
\newcommand{\subsubsecautorefname}{subsubsection}

\title{Biometric Authentication System Documentation} \author{Authors}
\date{\today}

\begin{document}

\maketitle
\newpage
\tableofcontents
\listoffigures
\newpage

\section{Introduction}
The Biometric Authentication System is a prove of concept of an IoT
solution designed to provide security authentication through biometric verification, including
galvanic skin response, heart rate analysis, and facial recognition. This
project's primary objective is to establish a user-friendly system
for authenticating individuals in secure environments as well as experimenting and learning with IoT devices. The following
documentation comprises detailed descriptions of system components,project milestones, a user story depicting the system's functionality, and
technical insights into the component integration and operation.

\section{General Project Milestones} The development of the Biometric
Authentication System was achieved through the accomplishment of several key
milestones. These milestones collectively ensured the project's progress was
systematically tracked and adhered to the proposed timeline. Note that component specific milestones with more
detailed information, priorities and dependencies can be found on \autoref{component-implementations}

\begin{enumerate} 
    \item \textbf{Project Initiation:} Defining scope, objectives,
and resource allocation. 
\item \textbf{Component Sourcing and Assembly:} Hardware setup of the development environment. 
\item \textbf{System Design:} Architecting overall system interactions and data flow.
\item \textbf{Component Integration:} Ensuring seamless operation between
different system modules. 
\item \textbf{Software Development:} Writing and
testing code for individual components and overall system coordination. 
\item \textbf{Project Wrap-Up:} Final evaluation, documentation,
and project delivery. 
\end{enumerate}

\section{Component Implementations}\label{sec:component-implementations} This section outlines the individual
components that comprise our system, detailing their objectives, functionalities,
and integration with the broader system context.

\input{raspberry.tex}
\input{activity_monitor.tex}
\input{user_data_collector.tex}
\input{presence.tex}

\section{User Story} As the user approaches the authentication system, he is
immediately detected by the ultrasonic sensors, which guide him to stand in the
optimal position for scanning. As he places his fingers on the biometric sensors,
his heart rate and skin resistance data are quietly collected and sent to the
Raspberry Pi. At the same moment, the user looks at the camera, and his facial
features are analyzed. The Raspberry Pi processes this information using
a neural network and merges the results of the facial prediction with the biometrics sensors
data by running them into a decision tree which outputs a final prediction, which appears on the screen
and will tell which of the authorized users matches with if any. Within seconds, if the system identifies the user, 
his name is displayed on the monitors.

\section{Final Project Conclusions} The development of the Biometric
Authentication System has been a path characterized by learning, adaptability,
and fighting with malfunctioning sensors. One of the main challenges was synchronizing data from various
biometric sensors with the real-time processing on the Raspberry Pi.
By applying concurrency principles we managed to overcome this challenges and end up with a significantly accurate system.

Overall, the system has realized robust biometric authentication with an
impressive accuracy rate. The modularity of the system design also allows for
easy updates and scalability.

For future work, we suggest exploring alternative biometric modalities such as
iris recognition or palm-print scanning to further enhance system security.
Additionally, implementing machine learning models with more extensive datasets
can offer continued improvement in recognition accuracy and pave the way for
personalized user experiences.

\newpage
\section{Technical Documentation}
For a in depth technical documentation of the system, detailed 
instructions on how to setup the system and how to use it, please refer to the following specifications
(which can also be found in the project repository):

\input{../technical-docs/rpi.tex}
\input{../technical-docs/linux-router.tex}
\end{document}
