\subsection{Phone App}

\subsubsection{Objective and Functionality}
The objective of this android app is to show the different data on an android app, which is better than a screen, since it can show more information.\footnote{The LCD display was too short for all the data we were sending.}

\subsubsection{Project Definition and Milestones}
\subsubsection{Achieved milestones, execution order, priority, and dependencies}
\begin{enumerate}
    \item \textbf{Milestone 1: Creating the UI}
        \begin{enumerate}
            \item \textit{Priority:} High. Fundamental for showing the data
            \item \textit{Dependencies:} None
            \item \textit{Execution Order:} First, as later we'll only have to pull the data.
            \item \textit{Assigned to:} Oriol
        \end{enumerate}

    \item \textbf{Milestone 2: Connecting the Android App to the MQTT Broker}
        \begin{enumerate}
            \item \textit{Priority:} High. Essential for functionallity
            \item \textit{Dependencies:} Successful MQTT setup (libraries).
            \item \textit{Execution Order:} Second, building upon creating the ui
            \item \textit{Assigned to:} Oriol
        \end{enumerate}

    \item \textbf{Milestone 3: Showing the data inside the app}
        \begin{enumerate}
            \item \textit{Priority:} High. Essential for functionallity
            \item \textit{Dependencies:} Successful MQTT setup (libraries) and creating the ui.
            \item \textit{Execution Order:} Third, building upon creating the ui and connecting to the broker
            \item \textit{Assigned to:} Oriol
        \end{enumerate}
\end{enumerate}

\subsubsection{Hardware setup}
None

\subsubsection{Dedication Time}
Approximately 8 hours were dedicated to developing android app, mainly spent on searching how the mqtt libraries work in kotlin and building the ui.

\subsubsection{Challenges and Solutions}
\begin{itemize}
    \item \textbf{Hardware Challenges:} None
    \item \textbf{Software Challenges:} The library methods weren't "kotlin friendly".
\end{itemize}
